SCPCL000822 - Validation of tumor cells

### 2024-06-17 analyses/cell-type-ewings/cell_type_annotations/SCPCS000490/SCPCL000822_tumor-cell-validation.Rmd
hide code and fix variable name typo in notebook

---
title: "SCPCL000822 - Validation of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
---

@@

```{r}
# export final TSV with annotations 
final_classifications <- new_classification_df |> 
  dplyr::select(
    cell_barcode = barcodes,
    tumor_cell_classification = combined_cnv_classification
  ) |> 
  unique()

>>>>

---
title: "SCPCL000822 - Validation of tumor cells"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    code_folding: hide
---

@@

```{r}
# export final TSV with annotations 
final_classifications <- classification_df |> 
  dplyr::select(
    cell_barcode = barcodes,
    tumor_cell_classification = combined_cnv_classification
  ) |> 
  unique()
